---
output: rmarkdown::github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "",
  fig.path = "inst/extdata/"
)
```

## `AMMIStbP`: Additive Main Effects and Multiplicative Interaction Model Stability Parameters

```{r,echo = FALSE, message = FALSE, eval = FALSE}
devtools::load_all(".")

```

###### Version : [`r getNamespaceVersion("AMMIStbP")`](https://ajaygpb.github.io/AMMIStbP/); License: [GPL-2|GPL-3](https://www.r-project.org/Licenses/)

##### *Ajay, B. C.^1^, Aravind, J.^2^, Abdul Fiyaz, R.^3^ and S. K. Bera^4^*

1. RRS, ICAR-Directorate of Groundnut Research, Anantapur 
2. ICAR-National Bureau of Plant Genetic Resources, New Delhi
3. ICAR-Indian Institute of Rice Research, Hyderabad
4. ICAR-Directorate of Groundnut Research, Junagadh

***
[![minimal R version](https://img.shields.io/badge/R>%3D-3.0.2-6666ff.svg)](https://cran.r-project.org/)
[![License: GPL v3](https://img.shields.io/badge/License-GPL%20v3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version-last-release/AMMIStbp)](https://cran.r-project.org/package=AMMIStbp)
<!-- [![rstudio mirror downloads](https://cranlogs.r-pkg.org/badges/grand-total/AMMIStbp?color=green)](https://CRAN.R-project.org/package=AMMIStbp) -->
<!-- [![packageversion](https://img.shields.io/badge/Package%20version-0.2.3.3-orange.svg)](https://github.com/ajaygpb/AMMIStbp) -->
[![develVersion](https://img.shields.io/badge/devel%20version-`r gsub("Version:\\s*", "", readLines(paste0("https://raw.githubusercontent.com/", "ajaygpb/AMMIStbp", "/master/DESCRIPTION"))[grep("Version:", readLines(paste0("https://raw.githubusercontent.com/", "ajaygpb/AMMIStbp", "/master/DESCRIPTION")))])`-orange.svg)](https://github.com/ajaygpb/AMMIStbp)
<!-- [![GitHub Download Count](https://github-basic-badges.herokuapp.com/downloads/ajaygpb/AMMIStbp/total.svg)] -->
[![Project Status: WIP](http://www.repostatus.org/badges/latest/wip.svg)](http://www.repostatus.org/#wip)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)
<!-- [![Rdoc](http://www.rdocumentation.org/badges/version/AMMIStbp)](http://www.rdocumentation.org/packages/AMMIStbp) -->
<!-- [![Zenodo DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.841963.svg)](https://doi.org/10.5281/zenodo.841963) -->
<!-- [![Analytics](https://pro-pulsar-193905.appspot.com/UA-116683292-1/welcome-page)](https://github.com/aravind-j/google-analytics-beacon) --> 



***

## Warning

Package is not stable at present. It is under development. Please use only after release of stable version.

## Installation

### Install development version from Github
```{r, eval=FALSE}
devtools::install_github("ajaygpb/AMMIStbP")
```

## Detailed tutorial
For a detailed tutorial on how to used this package type:

```{r, eval=FALSE}
browseVignettes(package = 'AMMIStbP')
```

## What's new
To know whats new in this version type:

```{r, eval=FALSE}
news(package='AMMIStbP')
```

## Links

<!-- [CRAN page](https://cran.r-project.org/package=AMMIStbP) -->

[Github page](https://github.com/ajaygpb/AMMIStbP)

<!-- [Github website](https://ajaygpb.github.io/AMMIStbP/) -->

<!-- [Zenodo DOI](https://doi.org/10.5281/zenodo.1310011) -->

## Citing `AMMIStbP`
To cite the methods in the package use:

```{r, eval = FALSE}
citation("AMMIStbP")
```

```{r, echo = FALSE}
detach("package:AMMIStbP", unload=TRUE)
suppressPackageStartupMessages(library(AMMIStbP))
cit <- citation("AMMIStbP")
# yr <- format(Sys.Date(), "%Y")
# cit[1]$year <- yr
# oc <- class(cit)
# 
# cit <- unclass(cit)
# attr(cit[[1]],"textVersion") <- gsub("\\(\\)",
#                                      paste("\\(", yr, "\\)", sep = ""),
#                                      attr(cit[[1]],"textVersion"))
# class(cit) <- oc
cit
```
