---
output: rmarkdown::github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "",
  fig.path = "inst/extdata/"
)
```

## `AMMIStbP`: Additive Main Effects and Multiplicative Interaction Model Stability Parameters

```{r,echo = FALSE, message = FALSE, eval = FALSE}
devtools::load_all(".")

```

###### Version : [`r getNamespaceVersion("AMMIStbP")`](https://ajaygpb.github.io/AMMIStbP/articles/Introduction.html#version-history); License: [GPL-2|GPL-3](https://www.r-project.org/Licenses/)

##### *Ajay, B. C.^1^, Aravind, J.^2^, and Abdul Fiyaz, R.^3^*

1. RRS, ICAR-Directorate of Groundnut Research, Anantapur 
2. ICAR-National Bureau of Plant Genetic Resources, New Delhi
3. ICAR-Indian Institute of Rice Research, Hyderabad

***



***

## Warning

Package is not stable at present. It is under development. Please use only after release of stable version.

## Installation

### Install development version from Github
```{r, eval=FALSE}
devtools::install_github("ajaygpb/AMMIStbP")
```

## Detailed tutorial
For a detailed tutorial on how to used this package type:

```{r, eval=FALSE}
browseVignettes(package = 'AMMIStbP')
```

## What's new
To know whats new in this version type:

```{r, eval=FALSE}
news(package='AMMIStbP')
```

## Links

## Citing `AMMIStbP`
To cite the methods in the package use:

```{r, eval = FALSE}
citation("AMMIStbP")
```

```{r, echo = FALSE}
cit <- citation("AMMIStbP")
yr <- format(Sys.Date(), "%Y")
cit[1]$year <- yr
oc <- class(cit)

cit <- unclass(cit)
attr(cit[[1]],"textVersion") <- gsub("\\(\\)",
                                     paste("\\(", yr, "\\)", sep = ""),
                                     attr(cit[[1]],"textVersion"))
class(cit) <- oc
cit
```
