---
title: "The **AMMIStbP** package: A brief introduction"
header-includes:
- \usepackage{fancyhdr}
- \usepackage{wrapfig}
- \pagestyle{fancy}
- \fancyhead[LE,RO]{\slshape \rightmark}
- \fancyhead[LO,RE]{The germinationmetrics package{:} A brief introduction}
- \fancyfoot[C]{\thepage}
- \usepackage{hyperref}
- \hypersetup{colorlinks=true}
- \hypersetup{linktoc=all}
- \hypersetup{linkcolor=blue}
- \usepackage{pdflscape}
- \usepackage{booktabs}
- \usepackage[table]{xcolor}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output:
  pdf_document:
    dev: cairo_pdf
    fig_caption: no
  html_document:
    df_print: paged
csl: frontiers.csl
bibliography: REFERENCES.bib
link-citations: yes
toc: no
vignette: |
  %\VignetteIndexEntry{Introduction}
  %\usepackage[utf8]{inputenc}
  %\VignetteEngine{knitr::rmarkdown_notangle}
---

\begin{center}
 {\it Ajay B. C., J. Aravind^2^ and R. Abdul Fiyaz}
\end{center}

\begin{center}
 1. RRS, ICAR-Directorate of Groundnut Research, Anantapur 
 2. ICAR-National Bureau of Plant Genetic Resources, New Delhi
 3. ICAR-Indian Institute of Rice Research, Hyderabad
\end{center}

\begin{center}
`r Sys.Date()`
\end{center}

\begin{center}
\vspace{6pt}
\hrule
\end{center}

```{r, echo = FALSE}
knitr::opts_chunk$set(
  comment = "",
  fig.cap = ""
)
```

\tableofcontents



The package `AMMIStbP` is .........

## Installation
The package can be installed using the following functions:

```{r, eval=FALSE}
# Install from CRAN
install.packages('AMMIStbP', dependencies=TRUE)

# Install development version from Github
devtools::install_github("ajaygpb/AMMIStbP")

```

Then the package can be loaded using the function
```{r}
library(AMMIStbP)
```

## AMMI

The AMMI equation

$$Y_{ijk} = \mu + \alpha_{i} + \beta_{j} + \sum_{k=1}^{N}\lambda_{k}\gamma_{ik}\delta_{jk} + \rho_{ij} + \varepsilon_{ijk}$$

Where, $Y_{ijk}$ is the yield of i^th^ genotype in environment E for replicate r, $\mu$ is the total yield mean, $\alpha_{i}$ is the mean deviation of i^th^ genotype (genotype mean minus total yield mean), $\beta_{j}$ is the mean deviation of j^th^ environment, $\lambda_{k}$ is the singular value for IPCA axis $N$, $\gamma_{ik}$ is the i^th^ genotype eigenvector value for IPCA axis $N$, $\delta_{jk}$ is the  j^th^ environment eigenvector value for IPCA axis $N$, $\rho_{ij}$ is the residual, and $\varepsilon_{ijk}$ is the error.

## AMMI stability parameters

The details about AMMI stability parameters/indices implemented in `AMMIStbP` are described in Table 1.

\newpage
\blandscape

\rowcolors{2}{gray!25}{white}
\renewcommand{\arraystretch}{1.3}

**Table 1 :** AMMI stability parameters/indices implemented in `AMMIStbP`.
\footnotesize
```{r, echo = FALSE, eval = TRUE}
load("stability.rda")

indices$`function` <- paste("`", indices$`function`, "`", sep = "")

# indices$Details <- gsub("\\r\\n\\r\\n", "$$\\\\, $$", indices$Details)
# indices$Details <- gsub("$$\\, $$$$", "$$", indices$Details, fixed = TRUE)
#indices$Details <- paste(indices$Details, "$$\\\\, $$", sep = "")

indices$Details <- gsub("\\r\\n", "\\\\\n", indices$Details)

#indices$Details <- gsub("\\r\\n\\r\\n", "##", indices$Details)
#indices$Details <- gsub("##", "\\\n", indices$Details)

indices$Reference <- gsub("\\[|\\]", "", indices$Reference)
#indices <- indices[-27,]

```


```{r, echo = FALSE, eval = TRUE}
pander::pander(indices, style='multiline',
               split.cell = c(15, 18, 50, 10, 10, 10),
               justify = c('left'), split.table = Inf, keep.line.breaks = TRUE,
               use.hyphening = FALSE, missing = "")
```

\elandscape

\newpage

#### Examples

## Citing `AMMIStbP`

```{r, echo = FALSE, collapse = TRUE}
suppressMessages(cit <- citation("AMMIStbP"))
yr <- format(Sys.Date(), "%Y")
cit[1]$year <- yr
oc <- class(cit)

cit <- unclass(cit)
attr(cit[[1]],"textVersion") <- gsub("\\(\\)",
                                     paste("\\(", yr, "\\)", sep = ""),
                                     attr(cit[[1]],"textVersion"))
class(cit) <- oc
cit
```

## Session Info

```{r}
sessionInfo()
```

## References
